Outputs - civil servants' survey

### 2024-12-22 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

Alternative Measure for Exit

@@

## Controls

@@

>>>>

Alternative Measure for Exit 
```{r}

@@

@@

Models with Junior Civil Servants
```{r}

## include junior
data_for_analysis_all <- new_data %>% 
  filter(INTENT_EXIT_2>0|
           PROJECT_EFFORT>0|
           PROJECT_VOICE>0)

exit_mod1 <- lm(INTENT_EXIT_2 ~ 
                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_all %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

```{r, fig.width=8,fig.height=6}
p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()

p1

#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
```
